---
title: "Report Group 2"
author: "Group 2"
date: "2024-02-28"
output:
  pdf_document:
    toc: yes
    number_sections: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment=NA,attr.source='.numberLines')

rm(list=ls())
library(readr)
library(RSQLite)
library(dplyr)
library(ggplot2)
library(lubridate)
library(treemapify)
library(maps)
library(mapproj)
library(gridExtra)
library(grid)
```

# Task 1.2: SQL Database Schema Creation
```{r connect}
# set up the connection
my_db <- RSQLite::dbConnect(RSQLite::SQLite(),"../database/ecommerce.db")
```

## CREATE tables 
````{bash, eval=FALSE}
# link to SQL file
sqlite3 "../database/ecommerce.db" < "../main/ecommerce.sql"
```

# For Initial load
## Validation and Load files in an sqlite database
```{r}
# Get only Initial file
all_files <- setdiff(list.files("../data_upload/"), list.files("../data_upload/", pattern = "_"))
# Order the files to load to database, to avoid error from foreign key
custom_order <- list("customers.csv","sellers.csv","categories.csv","products.csv","shippers.csv","orders.csv","advertisements.csv")
all_files <- all_files[order(match(all_files, custom_order))]

for (variable in all_files) {
  this_filepath <- paste0("../data_upload/",variable)
  this_file_contents <- readr::read_csv(this_filepath)

  table_name <- gsub(".csv","",variable)
  
  # Get the primary key column names from the database
  query <- paste("SELECT name FROM pragma_table_info('",table_name,"') WHERE pk = 1;",sep="")
  primary_key_columns <- dbGetQuery(my_db, query)
  
  # Get Foreign Key
  query <- paste("PRAGMA foreign_key_list('",table_name,"');",sep="")
  foreign_key_columns <- dbGetQuery(my_db, query)
  
  # Perform Validation
  source("Validation.R")
  
  # convert column date format
  if (table_name == 'orders') {
    this_file_contents['order_date'] <- lapply(this_file_contents['order_date'], as.character)
  }
  
  if (nrow(this_file_contents)>0 ){
      for (i in 1:nrow(this_file_contents)) {
        row <- this_file_contents[i, ]
        
        # Extract primary key values from the row
        primary_key_values <- paste(names(row)[names(row) %in% primary_key_columns], row[names(row) %in% primary_key_columns], sep = "=", collapse = " AND ")
        
        # Find if the primary key exists
        query <- paste("SELECT * FROM", table_name, paste("WHERE", primary_key_values))
        existing_row <- dbGetQuery(my_db, query)
        
        if (nrow(existing_row) == 0) {
          # Row is unique, append to the table
          #print(paste("Append:",primary_key_values))
          dbWriteTable(my_db, table_name, row, append = TRUE)
        } else {
          # Row already exists, update the existing row
          #print(paste("Update:",primary_key_values))
          update_query <- paste("UPDATE", table_name, paste("SET", paste(names(row), "=", paste0("'", row, "'"), collapse = ", "), "WHERE", primary_key_values))
          dbExecute(my_db, update_query)
        }
      }
    }
    else {
      print("Nothing to update in database since all rows are not pass the validations")
    }
  
  #RSQLite::dbWriteTable(my_db,table_name,this_file_contents,append=TRUE)
}

```


# Data Analysis 

## Create views for analysis

### View linked product, categories, sellers and advertisements

```{sql connection=my_db}
--Create a view for products linked to categories, sellers and advertisements
DROP VIEW IF EXISTS df_products;
```

```{sql connection=my_db}
CREATE VIEW IF NOT EXISTS df_products AS
SELECT p.id, p.seller_id, p.category_id, p.price, p.inventory,
s.name AS seller_name,
CONCAT(p.name, ' ID ', p.id) AS product_name,
SUM(a.ad_clicks) AS total_ad_clicks,
SUM(a.budget) AS total_budget,
cat.name AS category_name
FROM products as p
LEFT JOIN sellers s ON p.seller_id = s.id
LEFT JOIN categories cat On p.category_id = cat.id
LEFT JOIN advertisements a on p.id= a.product_id
GROUP BY p.id
```

```{r}
df_products <- dbGetQuery(my_db, "SELECT *
                              FROM df_products")
```


### View linked orders, customers and products (including ads and sellers details)

```{sql connection=my_db}
DROP VIEW IF EXISTS df_sales;
```

```{sql connection=my_db}
CREATE VIEW IF NOT EXISTS df_sales AS
SELECT o.id, o.customer_id, o.product_id, o.quantity, o.discount, o.order_date, o.rating_review, dfp.price,
round(o.quantity*(1-o.discount/100.00)*dfp.price,2) AS sales,
round(o.quantity*(o.discount/100.00)*dfp.price,2) AS discount_value,
round(o.quantity*1000000/dfp.total_ad_clicks,2) AS conversion_rate,
dfp.seller_id, dfp.seller_name, dfp.total_budget, dfp.product_name,dfp.category_name, 
CONCAT(first_name, ' ', last_name) AS customer_name
FROM orders AS o
LEFT JOIN df_products dfp ON o.product_id = dfp.id
LEFT JOIN customers c ON o.customer_id = c.id
```

```{r}

```



```{r}
df_sales <- dbGetQuery(my_db, "SELECT *
                              FROM df_sales")
```


```{r}
df_sales <- dbGetQuery(my_db, "SELECT o.id, o.customer_id, o.product_id, o.quantity, o.discount, o.order_date, o.rating_review, dfp.price,
round(o.quantity*(1-o.discount/100)*dfp.price,2) AS sales,
round(o.quantity*(o.discount/100)*dfp.price,2) AS discount_value,
round(o.quantity*1000000/dfp.total_ad_clicks,2) AS conversion_rate,
dfp.seller_id, dfp.seller_name, dfp.total_budget, dfp.product_name,dfp.category_name, 
CONCAT(first_name, ' ', last_name) AS customer_name
FROM orders AS o
LEFT JOIN df_products dfp ON o.product_id = dfp.id
LEFT JOIN customers c ON o.customer_id = c.id")
```




## Figure 1:  Number of Products by Categories

```{r}
## Categories with number of products in each category

category_products <- dbGetQuery(my_db, "SELECT c.name AS category_name, COUNT(p.id) AS num_products
                              FROM products AS p
                              INNER JOIN categories AS c ON p.category_id = c.id
                              GROUP BY p.category_id, c.name
                              ORDER BY num_products DESC
                              LIMIT 10")

( figure.1 <- category_products %>%
ggplot(aes(x = reorder(category_name, -num_products), y = num_products)) +
  geom_bar(stat = "identity", fill = "#4393C3", color = "black") +
  labs(title = "Number of Products by Categories",
       x = "Category Name",
       y = "Number of Products") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        plot.title = element_text(size = 14, hjust = 0.5),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.margin = margin(t = 0.5, r = 0.5, b = 1, l = 1, unit = "cm")) +  
  geom_text(aes(label = num_products), vjust = -0.3, size = 3, color = "black") )
```

## Figure 2: Number of Ad clicks by Categories

```{r}
## Categories with number of ad clicks in each category

category_adclicks <- dbGetQuery(my_db, "
  SELECT p.id, p.category_id, c.name AS category_name,
  SUM(a.ad_clicks) AS total_ad_clicks
  FROM products AS p
  INNER JOIN advertisements a ON p.id = a.product_id
  INNER JOIN categories c ON p.category_id = c.id 
  GROUP BY p.category_id, c.name
  ORDER BY total_ad_clicks DESC
")

( figure.2 <- category_adclicks %>%
ggplot(aes(x = reorder(category_name, -total_ad_clicks), y = total_ad_clicks/1000000)) +
  geom_bar(stat = "identity", fill = "#4393C3", color = "black") +
  labs(title = "Total Ad clicks (millions) by Categories",
       x = "Category Name",
       y = "Total Ad clicks") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        plot.title = element_text(size = 14, hjust = 0.5),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.margin = margin(t = 0.5, r = 0.5, b = 1, l = 1, unit = "cm")) +  # Specify margins
  geom_text(aes(label = round(total_ad_clicks/1000000,2)), vjust = -0.3, size = 3, color = "black") )  # Add labels for each bar
```

## Figure 3: Number of Customers by States

```{r}
# read customers table from sql
customers <- dbGetQuery(my_db, "
  SELECT *
  FROM customers
")

cust_geo <- customers %>% group_by(billing_address_state) %>% summarise(n = n())

if (require("maps")) {
states <- map_data("state")
cust_geo$region <- tolower(cust_geo$billing_address_state)
choro <- merge(states, cust_geo, sort = FALSE, by = "region")
choro <- choro[order(choro$order), ]
( figure.3 <- ggplot(choro, aes(long, lat)) +
  geom_polygon(aes(group = group, fill = n)) +
  coord_map("albers",  lat0 = 45.5, lat1 = 29.5) +
  scale_fill_continuous(trans = "reverse") +
  labs(title = "Number of Customers by States") +
  theme_minimal() +
  theme(legend.position = "left",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        plot.title = element_text(size = 14, hjust = 0.5),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.margin = margin(t = 0.5, r = 0.5, b = 1, l = 1, unit = "cm"))
 )
}
```

## Figure 4: Number of Sellers by States

```{r}
# read sellers table from sql
sellers <- dbGetQuery(my_db, "
  SELECT *
  FROM sellers
")

seller_geo <- sellers %>% group_by(address_state) %>% summarise(n = n())

if (require("maps")) {
states <- map_data("state")
seller_geo$region <- tolower(seller_geo$address_state)
choro <- merge(states, seller_geo, sort = FALSE, by = "region")
choro <- choro[order(choro$order), ]
( figure.4 <- ggplot(choro, aes(long, lat)) +
  geom_polygon(aes(group = group, fill = n)) +
  coord_map("albers",  lat0 = 45.5, lat1 = 29.5) +
  scale_fill_continuous(trans = "reverse") +
  labs(title = "Number of Sellers by States") +
  theme_minimal() +
  theme(legend.position = "left",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        plot.title = element_text(size = 14, hjust = 0.5),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        plot.margin = margin(t = 0.5, r = 0.5, b = 1, l = 1, unit = "cm"))
 )
}
```

## Dashboard 1: Platform Overview

```{r}
# Extract the date and time
this_filename_date <- as.character(Sys.Date())
this_filename_time <- as.character(format(Sys.time(), format = "%H_%M"))

# Combine charts and save as image
png(paste0("Visualisations/platform_overview",
              this_filename_date,"_",
              this_filename_time,".png"), width = 1200, height = 800)  
grid.arrange(figure.1, figure.2, figure.3, figure.4, nrow = 2,
             top = textGrob("Platform Overview",gp=gpar(fontsize=24,font=2)))
```

## Figure 5: Monthly Sales Analysis

```{r}
daily_sales <- dbGetQuery(my_db, "
  SELECT order_date, sales
  FROM df_sales
")

# Convert order_date to date format
daily_sales$order_date <- as.Date(daily_sales$order_date, format = "%Y-%m-%d")

# Aggregate by month
monthly_sales <- daily_sales %>%
  mutate(year_month = floor_date(order_date, "month")) %>%
  group_by(year_month) %>%
  summarise(sales = sum(sales)) %>%
  arrange(desc(year_month))

# Take last 12 months
monthly_sales <- head(monthly_sales, 12)

# Plot monthly sales trend with advanced visualization
( figure.5 <- ggplot(monthly_sales, aes(x = year_month, y = sales)) +
  geom_line(color = "blue", size = 1.5) +
  geom_point(color = "red", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  labs(title = "Monthly Sales Trend (last 12 months)", x = "Month", y = "Sales") +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 10)) + # Rotate x-axis labels vertically
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "$")) )
```

## Figure 6: Sales by Categories

```{r}
sales_by_category <- dbGetQuery(my_db, "
  SELECT category_name, SUM(sales) AS total_sales
  FROM df_sales
  GROUP BY category_name
")

( figure.6 <- sales_by_category %>%
  ggplot(aes(area = total_sales, fill = category_name, label = paste0(category_name, "\n", scales::dollar(total_sales)))) +
  geom_treemap() +
  geom_treemap_text(fontface = "bold", place = "centre", grow = TRUE, reflow = TRUE, color = "lightgrey") + 
  scale_fill_viridis_d() +  
  labs(title = "Sales by Categories",
       fill = "Category",
       caption = "Sales values are in USD") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.caption = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold")) )
```

## Figure 7: Top 10 Customers by Amount Spent

```{r}
top_customers <- dbGetQuery(my_db,
  "SELECT CONCAT(customer_name, ' ID ', customer_id) AS customer_name, sales 
  FROM df_sales
  GROUP BY customer_name
  ORDER BY sales DESC
  LIMIT 10"
)

( figure.7 <- top_customers %>%
arrange(desc(sales)) %>%
ggplot(aes(x = reorder(customer_name, sales), y = sales, fill = customer_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Customers by Total Sales",
       x = "Customer",
       y = "Total Sales") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3") +
  geom_text(aes(label = sales), size = 4, color = "black") +
  coord_flip() )
```

## Figure 8. Top 10 Sellers by Total Sales

```{r}

top_sellers <- dbGetQuery(my_db,
  "SELECT CONCAT(seller_name, ' ID ', seller_id) AS seller_name, sales 
  FROM df_sales
  GROUP BY seller_name
  ORDER BY sales DESC
  LIMIT 10")

( figure.8 <- top_sellers %>%
arrange(desc(sales)) %>%
ggplot(aes(x = reorder(seller_name, sales), y = sales, fill = seller_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Sellers by Total Sales",
       x = "Seller",
       y = "Total Sales") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
        scale_fill_brewer(palette = "Set3") +
        geom_text(aes(label = sales), size = 4, color = "black") +
        coord_flip() )
```

## Dashboard 2: Sales Performance

```{r}
# Extract the date and time
this_filename_date <- as.character(Sys.Date())
this_filename_time <- as.character(format(Sys.time(), format = "%H_%M"))

# Combine charts and save as image
png(paste0("Visualisations/sales_performance",
              this_filename_date,"_",
              this_filename_time,".png"), width = 1200, height = 800)  
grid.arrange(figure.5, figure.6, figure.7, figure.8, nrow = 2,
             top = textGrob("Sales Performance",gp=gpar(fontsize=24,font=2)))
```

## Figure 9: Top 10 Selling Products by Value

```{r}
top_products <- dbGetQuery(my_db,
  "SELECT product_name, SUM(sales) AS total_sales
  FROM df_sales
  GROUP BY product_name
  ORDER BY total_sales DESC
  LIMIT 10")


( figure.9 <- top_products %>%
  ggplot(aes(x = reorder(product_name, total_sales), y = total_sales, fill = product_name)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Top 10 Selling Products by Value",
       x = "Product",
       y = "Total Sales") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3") +
  coord_flip() +  # Flip the coordinates to make horizontal bars
  geom_text(aes(label = total_sales), vjust = -0.3, size = 4, color = "black", fontface = "bold") )
```

## Figure 10: Top 10 Selling Products by Quantity

```{r}
top_products_q <- dbGetQuery(my_db,
  "SELECT product_name, SUM(quantity) AS total_sold
  FROM df_sales
  GROUP BY product_name
  ORDER BY total_sold DESC
  LIMIT 10")

( figure.10 <- top_products_q %>%
  ggplot(aes(x = reorder(product_name, total_sold), y = total_sold, fill = product_name)) +
  geom_bar(stat = "identity", color = "black") +
  scale_fill_brewer(palette = "Paired") +  # Using a built-in palette
  labs(title = "Top 10 Selling Products by Quantity",
       x = "Product",
       y = "Total Quantity Sold") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3") +
  coord_flip() +  # Flip the coordinates to make horizontal bars
  geom_text(aes(label = total_sold), vjust = -0.3, size = 4, color = "black", fontface = "bold") )
```

## Figure 11: Top & Bottom 5 Rating Products


```{r}
top_products_r <- dbGetQuery(my_db,
  "SELECT product_name, rating_review
  FROM df_sales
  WHERE rating_review BETWEEN 1 AND 5")

top_products_r <- top_products_r %>% group_by(product_name) %>% summarise (average_rating = round(sum(rating_review)/n(),2)) %>% arrange(desc(average_rating))  
top_5_rating <- head(top_products_r,5)
bottom_5_rating <- tail(top_products_r,5)
top_bottom_5_rating <-rbind(top_5_rating,bottom_5_rating)

( figure.11 <- top_bottom_5_rating %>%
  ggplot(aes(x = reorder(product_name, average_rating), y = average_rating, fill = product_name)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Top & Bottom 5 Rating Products",
       x = "Product",
       y = "Average Rating") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3") +
  coord_flip() +  # Flip the coordinates to make horizontal bars
  geom_text(aes(label = average_rating), vjust = -0.3, size = 4, color = "black", fontface = "bold") )
```

## Figure 12: Top 10 Products by Ad clicks to Sales Conversion

```{r}
top_products_c <- dbGetQuery(my_db,
  "SELECT product_name, SUM(conversion_rate) as total_conversion_rate
  FROM df_sales
  WHERE conversion_rate IS NOT NULL
  GROUP BY product_name
  ORDER BY total_conversion_rate DESC
  LIMIT 10")


( figure.12 <- top_products_c %>%
  ggplot(aes(x = reorder(product_name, total_conversion_rate), y = total_conversion_rate, fill = product_name)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Total Conversion Rate",
       x = "Product",
       y = "Conversion Rate (sales quality/million ad clicks)") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 12, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none") +
  scale_fill_brewer(palette = "Set3") +
  coord_flip() +  # Flip the coordinates to make horizontal bars
  geom_text(aes(label = total_conversion_rate), vjust = -0.3, size = 4, color = "black", fontface = "bold") )
```

## Dashboard 3: Top Products

```{r}
# Extract the date and time
this_filename_date <- as.character(Sys.Date())
this_filename_time <- as.character(format(Sys.time(), format = "%H_%M"))

# Combine charts and save as image
png(paste0("Visualisations/top_products",
              this_filename_date,"_",
              this_filename_time,".png"), width = 1200, height = 800)  
grid.arrange(figure.9, figure.10, figure.11, figure.12, nrow = 2,
             top = textGrob("Top Products",gp=gpar(fontsize=24,font=2)))
```

## Figure 13: Average Rating by Months


```{r}
rating_y <- dbGetQuery(my_db,
  "SELECT id, product_name, order_date, rating_review, sales
  FROM df_sales
  WHERE rating_review BETWEEN 1 AND 5")

# Convert order_date to date format
rating_y$order_date <- as.Date(rating_y$order_date, format = "%Y-%m-%d")
rating_y <- rating_y %>% mutate(year_month = floor_date(order_date, "month"))

# Calculate the average   
rating_y_sum <- rating_y %>% group_by(year_month) %>% summarise (n_y = n(), average_rating = round(sum(rating_review)/n(),2)) %>% arrange(desc(year_month)) 

test <- rating_y %>% group_by(rating_review) %>% summarise(sales = sum(sales))
# Take last 12 months
rating_y_sum <- head(rating_y_sum,12)


# Plot monthly sales trend with advanced visualization
( figure.13 <- ggplot(rating_y_sum, aes(x = year_month, y = average_rating)) +
  geom_line(color = "blue", size = 1.5) +
  geom_point(color = "red", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  labs(title = "Monthly Average Rating (last 12 months)", x = "Month", y = "Average Rating") +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 10)) + # Rotate x-axis labels vertically
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") )
```


## Figure 14: Percentage of Nil Rating

```{r}
rating_all <- dbGetQuery(my_db,
  "SELECT id, product_name, order_date, rating_review, sales
  FROM df_sales")

# Convert order_date to date format
rating_all$order_date <- as.Date(rating_all$order_date, format = "%Y-%m-%d")
rating_all <- rating_all %>% mutate(year_month = floor_date(order_date, "month"))

# Calculate total number of orders per months
rating_all_summary <- rating_all %>% group_by(year_month) %>% summarise (n_all = n())

# Filter no rating and convert date format
rating_n <- rating_all %>% filter(rating_review == "NA") 

# Calculate number of orders with no review 
rating_n_summary <- rating_n %>% group_by(year_month) %>% summarise (n_n = n()) 

# Combine data
rating_n_summary <- merge(rating_all_summary, rating_n_summary)

# Calculate nil review rate
rating_n_summary <- rating_n_summary %>% mutate(nil_review_rate = n_n *100/n_all) %>% arrange(desc(year_month))

# Take last 12 months
rating_n_summary <- head(rating_n_summary,12)

# Plot monthly sales trend with advanced visualization
( figure.14 <- ggplot(rating_n_summary, aes(x = year_month, y = nil_review_rate)) +
  geom_line(color = "blue", size = 1.5) +
  geom_point(color = "red", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "darkgreen", linetype = "dashed") +
  labs(title = "Percentage of Nil Review (last 12 months)", x = "Month", y = "% of Nil Review") +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 10)) + # Rotate x-axis labels vertically
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") )
```

## Figure 15: Revenues by Rating Review

```{r}
revenue_by_rating_y <- rating_y %>% group_by(rating_review) %>% summarise(sales = sum(sales))
revenue_by_rating_n <- rating_n %>% group_by(rating_review) %>% summarise(sales = sum(sales))
revenue_by_rating <- rbind(revenue_by_rating_y, revenue_by_rating_n)

( figure.15 <- revenue_by_rating %>% 
  ggplot(aes(area = sales, fill = rating_review, label = paste0("Rating ", rating_review, "\n", scales::dollar(sales)))) +
  geom_treemap() +
  geom_treemap_text(fontface = "bold", place = "centre", grow = TRUE, reflow = TRUE, color = "lightgrey") + 
  scale_fill_viridis_d() +  
  labs(title = "Sales by Rating",
       fill = "Rating Review",
       caption = "Sales values are in USD") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.caption = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold")) )
```

## Figure 16: Average Discount by Month

```{r}
discount <- dbGetQuery(my_db, "
  SELECT order_date, discount_value, sales
  FROM df_sales
")

# Convert order_date to date format
discount$order_date <- as.Date(discount$order_date, format = "%Y-%m-%d")

# Aggregate by month
discount <- discount %>%
  mutate(year_month = floor_date(order_date, "month")) %>%
  group_by(year_month) %>%
  summarise(sales = sum(sales), discount_value = sum(discount_value), average_discount = discount_value/sales) %>%
  arrange(desc(year_month))

# Take last 12 months
discount <- head(discount, 12)

# Plot monthly sales trend with advanced visualization
( figure.16 <- ggplot(discount, aes(x = year_month, y = average_discount)) +
  geom_bar(stat = "identity", color = "black") + 
  labs(title = "Monthly Average Discount (last 12 months)", x = "Month", y = "Average Rating") +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 10, color = "black"),
        axis.title = element_text(size = 12, color = "black", face = "bold"),
        plot.title = element_text(size = 16, color = "black", face = "bold"),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 10)) + # Rotate x-axis labels vertically
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") )
```



## Dashboard 4: Customer Satisfaction

```{r}
# Extract the date and time
this_filename_date <- as.character(Sys.Date())
this_filename_time <- as.character(format(Sys.time(), format = "%H_%M"))

# Combine charts and save as image
png(paste0("Visualisations/customer_satisfaction",
              this_filename_date,"_",
              this_filename_time,".png"), width = 1200, height = 800)  
grid.arrange(figure.13, figure.14, figure.15, figure.16, ncol = 2,
             top = textGrob("Customer Statisfaction",gp=gpar(fontsize=24,font=2)))
```

Close Connection
```{r disconnect}
# Disconnect from the database using the connection variable that we setup 
# before
RSQLite::dbDisconnect(my_db)
```





